### 2024-01-11 inst/scripts/testDemo.Rmd
to try

ip=1:N
names(ip)=ip
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(endrepro-5,1), community=sample.int(K,1), sex=sample(c("F","M"),1), repro=FALSE, partner=-1))

pos=random2Dgrid(K=K,Gx=100)
initcomus=initialiseCommunities(traits=a,coordinates=pos)
size=table(sapply(population,"[[","community"))
initcomus$size=size
plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))

@@

quick=modelOOstyle( K =K, m=m, b=b, r=r, rho=rho, d=d, maturity=maturity, endrepro=endrepro, population=population, comus=initcomus, tstep=tstep, neutraltraitsParam=neutraltraitsParam, logging=c("na"),ma=endrepro-maturity)

@@

>>>>

ip=1:N
names(ip)=ip
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(endrepro-5,1), community=sample.int(K,1), sex=sample(c("F","M"),1), repro=FALSE, partner=-1))
                                      population=cbind(newpop(N,age="random",community = communities),initNeutralTraits(N,z))

pos=random2Dgrid(K=K,Gx=2)
initcomus=initialiseCommunities(traits=a,coordinates=pos,G=2,plot=T)
size=table(sapply(population,"[[","community"))
initcomus$size=size
plot(initcomus$coordinates,pch=21,bg=apply(initcomus$adaptivetraits,1,mean)+1,cex=log(initcomus$size))

@@

quick=modelVector( K =K, m=m, b=b, r=r, rho=rho, d=d, maturity=maturity, endrepro=endrepro, population=population, comus=initcomus, tstep=tstep, tp=neutraltraitsParam, logging=c("na"),ma=1,F_Th=NULL)

@@

```{r}
m=1
b=0.2
r=0.05
tstep=300
d=0.001
N=200
ip=1:N
names(ip)=ip
z=4 #number of neutral traits
neutraltraitsParam=initNeutralTraitsPathways(z = z)
neutraltraitsParam$s=c(0,0,1,1)
population=lapply(ip,function(i) list( id=as.character(i), traits=sample(c(0,1),size=z,replace=T), age=sample.int(65,1), community=1, sex=sample(c("F","M"),1), repro=FALSE, partner=-1))

neutraltraitsParam=initNeutralTraitsPathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=2)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=2,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),initNeutralTraits(N,z))
quickV=modelVector(K=K, m=1, b=0.1, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z))

alldeath=replicate(100,length(modelVector(K=K, m=1, b=0, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize"),logging=NULL,ma=1,traitsid=paste0("t",1:z))$popsize))

alldeath2=replicate(100,length(modelVector(K=K, m=1, b=0.1, r=0, rho=.5, d=0.04, maturity=18, endrepro=85, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize"),logging=NULL,ma=1,traitsid=paste0("t",1:z))$popsize))
boxplot(alldeath,alldeath2)

modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=1000, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize"),logging=NULL,ma=1,traitsid=paste0("t",1:z))$births
boxplot(alldeath,alldeath2)

initcomus$occupation[,]=1
testres=modelVector(K=K, m=1, b=0.8, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=800, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize","finalpop"),logging="time",ma=1,traitsid=paste0("t",1:z),F_Th=50)

population=testres$population
rmid=population[population[,"fid"]==-1,"id"]
population=population[population[,"fid"]!=-1,]
population=population[!(population[,"partner"]%in% rmid),]
initcomus$size=unname(table(population[,"community"]))
population=resetIds(population)

nrow(population[validCouple(population, maturity=18, endrepro=65),])
multirep=replicate(10,modelVector(K=K, m=1, b=10*0.04, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize","finalpop","repros"),logging="time",ma=1,traitsid=paste0("t",1:z)))

newtestres=modelVector(K=K, m=1, b=0.5, r=0, rho=.5, d=0.043, maturity=18, endrepro=65, population=testres$population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging="time",ma=1,traitsid=paste0("t",1:z))
plot(newtestres$deaths)
par(mfrow=c(3,2))
plot(newtestres$popsize,main="population size")
plot(newtestres$repro,main="number of valid couple")
plot(newtestres$popsize[-1],newtestres$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")
plot(newtestres$popsize[-1],newtestres$repros,xlab="population size",ylab=,main="#parents vs popsize")
plot(newtestres$repros/newtestres$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2)

plot(newtestres$popsize[-1],newtestres$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
for(repil in 1:ncol(multirep)) points(multirep[,repil]$popsize[-1],multirep[,repil]$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")

par(mfrow=c(3,2))
exp=newtestres
plot(exp$popsize,main="population size",xlab="time",ylab="# number individual",log="y",ylim=c(1,10000),type="l",lwd=2)
for(repil in 1:ncol(multirep)) lines(multirep[,repil]$popsize,,main="#death vs popsize",col=repil,lwd=2)
plot(newtestres$repro,main="number of valid couple",type="l",log="y",lwd=2,ylim=c(1,2000))
for(repil in 1:ncol(multirep)) 
lines(multirep[,repil]$repro,main="number of valid couple",col=repil,type="l",lwd=2)
plot(newtestres$popsize[-1],newtestres$deaths,xlab="population size",ylab="number of death",main="#death vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$deaths,xlab="population size",ylab="number of death",main="#death vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$births,xlab="population size",ylab="number of birth",main="#birth vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$repros,xlab="population size",ylab="number parents",main="#parents vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$repros,col=repil)
plot(newtestres$repros/newtestres$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,ylim=c(0,.5))
for(repil in 1:ncol(multirep)) 
lines(multirep[,repil]$repros/multirep[,repil]$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,col=repil)

multirep=sapply(,modelVector(K=K, m=1, b=10*0.04, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("births","deaths","popsize","finalpop","repros"),logging="time",ma=1,traitsid=paste0("t",1:z)))

newtestres=modelVector(K=K, m=1, b=0.5, r=0, rho=.5, d=0.043, maturity=18, endrepro=65, population=testres$population, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("repros","births","deaths","popsize","finalpop"),logging=c("time","visu"),ma=1,traitsid=paste0("t",1:z),F_Th = 60)

neutraltraitsParam=initNeutralTraitsPathways(z = 2)
traitsid=paste0("t",1:2)
percomu=50
K=2
km=0
ki=2
N=100
pos=random2Dgrid(K=K,Gx=5)
a=initAdaptiveTraits(ki=ki,km=km,n=1 )
initcomus=initialiseCommunities(ki=2,km=0,traits=a,coordinates=pos,G=5,plot=T,sizes=c(50,50))
communities=unlist(lapply(1:K,function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(N,age="random",community = communities),initNeutralTraits(N,z))
initcomus$size=unname(table(smallpop[,"community"]))
multrep=replicate(10,modelVector(K=K, m=1, b=0.39, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("finalpop","deaths","popsize","popfull","repros","births"),logging=c("time","fission"),ma=1,traitsid=paste0("t",1:z),F_Th=180))

plot(quickV$popsize)
plot(quickV$births)
plot(quickV$deaths)
plot(quickV$repros/quickV$popsize[-1],type="l")

par(mfrow=c(3,2))
plot(1,1,main="population size",xlab="time",ylab="# number individual",log="y",ylim=c(1,5000),type="l",lwd=2,xlim=c(0,501))
for(repil in 1:ncol(multirep)) lines(multirep[,repil]$popsize,,main="#death vs popsize",col=repil,lwd=2)
plot(1,1,main="number of valid couple",type="l",log="y",lwd=2,ylim=c(1,2000),xlim=c(0,501))
for(repil in 1:ncol(multirep)) lines(multirep[,repil]$repro,main="number of valid couple",col=repil,type="l",lwd=2)
plot(1,1,xlab="population size",ylab="number of death",main="#death vs popsize",ylim=c(1,100),xlim=c(0,500))
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$deaths,xlab="population size",ylab="number of death",main="#death vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$births,xlab="population size",ylab="number of birth",main="#birth vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$births,xlab="population size",ylab="number of birth",main="#birth vs popsize",col=repil)
plot(newtestres$popsize[-1],newtestres$repros,xlab="population size",ylab="number parents",main="#parents vs popsize")
for(repil in 1:ncol(multirep)) 
points(multirep[,repil]$popsize[-1],multirep[,repil]$repros,col=repil)
plot(newtestres$repros/newtestres$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,ylim=c(0,.5))
for(repil in 1:ncol(multirep)) 
lines(multirep[,repil]$repros/multirep[,repil]$popsize[-1],xlab="time",ylab="% people in valid couple",main="% parents",type="l",lwd=2,col=repil)

bs=round(runif(100,.35,.41),digit=2)
library(parallel)
cl<-makeCluster(10,type="FORK",outfile="log.txt")
allpopsiz=parSapply(cl,bs,function(b){
           res=modelVector(K=K, m=1, b=b, r=0, rho=.5, d=0.04, maturity=18, endrepro=65, population=smallpop, comus=initcomus, tstep=500, tp=neutraltraitsParam,age.threshold=20, out=c("popsize"),logging=c("done"),ma=1,traitsid=paste0("t",1:z),F_Th=180)
           res$popsize[length(res$popsize)]
})
stopCluster(cl)
